
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
\def\personal{%
\section*{Personal}

\begin{itemize}
\item Permanent resident in the United Kingdom. Japanese national.
\end{itemize}}

\def\education{%
\section*{Education}

\begin{itemize}
  \item Ph.D. Computational Linguistics, King's College London, U.K., 2008.

  \item M.Sc. Computational Linguistics (with Distinction), King's College London, U.K., 2003.

  \item Diploma in Computing, Open University, U.K., 2000.

  \item M.A. Applied Linguistics, Birkbeck College London, U.K., 1998.


  \item B.A. Philosophy, Waseda University, Japan, 1990.
\end{itemize}}


\def\languages{\section*{Language skills}
\begin{itemize}
\item Japanese (native): Lived in Japan for 25 years from birth. The
  language of daily use at home.

\vspace{-1mm}

\item  English (fluent): Have been living in London for 20 years. The language of
  daily use at work. Also the language in which I completed my higher
  degrees and conduct academic research.

\vspace{-1mm}

\item  French (advanced): Language of daily use for 4 years while living in France. Certified B2.

\vspace{-1mm}

\item  Korean (intermediate): Have been learning for five years. Can read documents
  and conduct basic conversations.
\end{itemize}

}



\def\computer{\section*{Computer skills}

Programming languages: Python, Prolog, Perl, C$^{++}$\\
OS: Unix (Linux) system operations and shell scripting\\
Text processing: sed, awk, Perl and Python\\
Other tools: \LaTeX, Git, NLTK, Weka, RNNLM

\def\researchWeb{{\tt\small http://homepages.stca.herts.ac.uk/\textasciitilde{}ys08aah}}
\def\papersWeb{\researchWeb{}{\tt\small /papers.html}}



%\def\publications_j{\section*{主要論文}

%\noindent{\smaller (全論文リストは\papersWeb{}を参照ください。またPDFのダウンロードが可能です。)}
%\bigskip
%{\fontspec{DejaVu Serif}
%\papers
%}
%}

