\documentclass[a4paper]{article}

\usepackage{cv}

\addtolength{\topmargin}{-.7cm}
\addtolength{\textheight}{4cm}
\addtolength{\oddsidemargin}{-.2cm}
\addtolength{\evensidemargin}{-.2cm}
%\addtolength{}{}

\def\name{Yo Sato}
\def\version{general}

\include{cv-common}

\include{publications}

\begin{document}

% Place name at left
{\huge \name}

\smallskip

Ph.D. and M.Sc. in Computational Linguistics, M.A. in Applied Linguistics\\
Qualified Translator (English $\rightarrow$ Japanese)\\
Permanent resident in the United Kingdom. Japanese national.

\bigskip

\begin{minipage}{0.3\linewidth}
  21 Coombe Gardens\\
  New Malden\\
  KT3 4AB
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone/Fax: &  (+44) (0)20-8288-1419 \\
    Email: & {\tt satoama@gmail.com} \\
    Websites:     & {\tt\small http://www.satoama.co.uk/yo}
  \end{tabular}
\end{minipage}


%\personal{}

%\vspace{-6mm}

\education{}

\vspace{-5mm}

\section*{Employment}

\begin{itemize}

\item \hspace{-2mm}Natural Language Processing Research Engineer, Nuance Communications U.K., Nov 2016--to date.

\hspace{-2mm}Duties: Building natural language understanding models principally for Japanese for the use of speech recognition engine. 


\item \hspace{-2mm}Natural Language Processing Research Engineer, MyScript Lab,  Aug 2012--Sep 2016.

\hspace{-2mm}Duties: Building principally statistical language models for handwriting recognition and input comple- tion and prediction. Main responsibilities include: morphological processing and learning algorighms based on corpora, as applicable to a wide range of languages (but with a special focus on Japanese and Korean); various N-Gram modelling with multi-word expression detection capability; adaptation of models to individuals and dialects

\item \hspace{-.2cm}Research Fellow in Computational Linguistics,
  University of Hertfordshire, Jan 2009--Mar 2012. 

\hspace{-.2cm}Duties: Building a language acquisition model, in particular grammar induction and phonological word discovery algorithms, for `ITALK' (Integration and Transfer of Action and Language Knowledge in Robots), a European FP7 Framework Project

\item \hspace{-.2cm}Research Assistant, Computer Science Dept, Queen
  Mary University of London, Jan 2008--Jan 2009.

\hspace{-.2cm}Duties: Implementing a parser that handles constructions typical in dialogue, such as ellipsis, based on the Dynamic Syntax formalism, for `Dynamics of Conversational
Dialogue', an Economic and Social Science Research Council (UK)
project. 

\item\hspace{-.2cm}Japanese Service, BBC World Television, 1996--2002

Duties: Translation and coordination related to the BBC news and documentary services, including simultaneous interpreting of news and subtitling and voice-over of documentary programmes  

\end{itemize}

\section*{Qualifications and skills}

\subsection*{Language skills}
\begin{itemize}
\item Japanese (native): Lived in Japan for 25 years from birth. The
  language of daily use at home.

\vspace{-1mm}

\item  English (fluent): Living in England for 20 years. The language of
  daily use at work. Also the language in which I completed my higher
  degrees and conduct academic research.

\vspace{-1mm}

\item  French (advanced): Language of daily use for 4 years while living in France. Certified B2.

\vspace{-1mm}

\item  Korean (intermediate): Learning for five years. Can read documents
  and conduct basic conversations.
\end{itemize}

\subsection*{General computer skills}

\begin{itemize}
 \item OS: Unix (Linux) system operations and shell scripting\\
  Programming languages: Python, Prolog, C$^{++}$, Java\\
  Web: HTML5 and Javascript, Apache server administration
   Other tools: SQL, \LaTeX, Git, XML

\end{itemize}

\subsection*{Language processing skills}

\begin{itemize}
\item Constraint-based grammar and parser building (with Prolog and Python)\\
  Text processing with Python, awk and sed\\
  Speech processing: acoustic model creation, recognition and forced alignment with HTK\\
  % Phonetics/phonology: phonemic transctiption, speech (including  prosodic) analysis with Praat\\
  Statistical language learning: probabilistic grammar (PCFG) learning from annotated corpora, N-gram based word prediction from unannotated corpora

%inference (Bayesian or Frequentist), significance tests and logistic regression with R\\
%  Machine learning (kNN with TiMBL, Bayesian or other
%  classification/clustering with WEKA)
%\end{itemize}

\end{itemize}
\vspace{-5mm}

\subsection*{Professional membership}

\begin{itemize}
\item Qualified Member, Institute of Translation and
  Interpreting, U.K. (English to Japanese, since 2002)\\
Member, Association of Computational Linguistics (ACL)
\\
 Member, Linguistics Association of Great Britain (LAGB)
\end{itemize}

\vspace{-4mm}

\section*{Academic profile}

\vspace{-1mm}

\subsection*{Key interests}

\begin{itemize}
\item Computational modelling of language acquisition
  (phonology, semantics and syntax)\\ Natural
  language parsing\\ Syntax, semantics and their interface (HPSG,
  Dynamic Syntax, Montague Grammar)\\Information structure of Japanese

\end{itemize}

\vspace{-4mm}

\subsection*{Teaching posts}

\begin{itemize}

\item Lecturer/tutor, Imperial College London,  2003--to date\\
   M.Sc. in Scientific, Technical and Medical Translation \\
   Language Technology Module and English-Japanese Practical Translation Module

\item Teaching Assistant, King's College London. 2005--2006.\\
    B.Sc. module `Natural Language Processing in Prolog' by Professor S. Lappin.\\
   Tutorials, lectures and exam setting/marking

\vspace{-4mm}

%\item Tutor, Bath University, 2006--2008, U.K.\\
%   M.A. in Translation Studies, \\Supervision on dissertations.


\end{itemize}
%%===========================================================================%%

\vspace{-3mm}
\subsection*{Selected publications}

\papersshort{}

\vspace{-4mm}

%%---------------------------------------------------------------------------%%

%\section*{Interests}
%Cricket, Cooking, Classical music




\end{itemize}




% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today
%\\A more updated version may be available at: \\
 %   \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
